Supplementary Materials

### 2019-01-17 sup_mat/sup_mat.Rmd
some text edits

# Methods 
The experiment took part over two sessions both lasting approximately 1 hour. All participants reported normal or corrected to normal vision and were from the University of Aberdeen. Participants were either compensated with course credit or £15 for their time. All participants gave informed consent.

All tasks were completed on a 17-inch CRT monitor with a resolution of 1400$x$1050 (*n* = 40) or 1600$x$1200 (*n* = 24). All tasks were programmed in MATLAB using the psychophysics and eyelink toolboxes.

## Split-Half
In this task, a chin rest with forehead bar was used in order to ensure a viewing distance of 47cm. Participants' fixations were tracked using a deskmounted Eylink 1000 (version 4.594) to record eye position at 1000 Hz. Prior to every block, a 9-point calibration was carried out. This task lasted approximately 30 minutes and was carried out in both sessions

Participants were instructed to state the presence, or absence, of a small target line segment that was tilted 45&deg; to the right. The distractor line segments were arranged in such a way to create a "hard" and "easy" search side. All distractors were orthogonal to the target with either a low variance (18&deg;) which created a relatively homogenous texture ("easy" side), or a high amount of variance (95&deg;) creating a more heterogenous texture ("hard" side). The line segments subtended approximately 1.6&deg; of visual angle. For 50% of the trials, there was a target present. Particiapnts were told to establish whether the target was present or absent on each trial as quickly and as accuractely as possible.

@@

## Adaptive Choice
For this task, participants were sat approximately 47cm from the screen though no chin rest was used to ensure a constant viewing distance. The search display consisted of small red, blue, and green squares arranged in three rings around a fixation point. the squares subtended between ~1.1&deg; and ~1.3&deg; depending on the screen resolution the participant was tested at (either 1600$x$1200 or 1400$x$1050, respectively). The participants' task was to find the blue or red square that contained the a number between 2 and 5 inclusive. On every trial there, both target colour squares contained a number between 2 and 5, but participants were told they only needed to report one of them. To ensure we could tell which colour they had decided, the blue and red target squares would always have a different number. The distractor blue and red squares would always contain a number between 6 and 9. The green squares contained numbers between 2 and 9. Again, they were instructed to complete the task as quickly and as accurately as possible.

Before starting the task, participants weregiven 10 practice trials and were free to ask any questions before starting the main expriment. If a participant was to report a number that was not in one of the two target boxes, a tone would sound to alert them to their mistake.

At the beginning of the experiment, there would be more red than blue squares (**need to check this is accuracte**) for five trials. Then, across the next seven trials, these would gradually change from red to blue, stay blue for five, and change etc. After completing the task, participants were then asked to fill out a short 3 item question asking them about their strategy and whether they noticed the gradual shift from one colour being the majority to the other.

## Foraging 
Same as the in the Adaptive Choice task, participants were not sat in a chin rest and so viewing distance was approximately 47cm. In this task, participants were presented with 84 small objects on the screen which subtended between ~0.6&deg; and ~0.7&deg; depending on the screen resolution the participant was tested at (either 1600$x$1200 or 1400$x$1050, respectively). Half of these were target items that participants were to click on until they had collected all of them. There were two types of search with this task. Either a feature search in which participants were presented with circles of 4 different colours (red, blue, yellow, and green) in which they were to click on all circles of two of the colours (e.g. click on the red and green, not the blue and yellow). The other being a conjunction search in which there were squares and circles coloured with two of the four possible colours, for example, they could be tasked with clicking on the blue squares and yellow circles, but try to avoid the blue circles and yellow squares. Participants completed both of these and the order was counterbalanced with the colours of the targets being randomised.

Before starting the experiment, participants had 5 practice trials to familiarise themeselves with the task, after which they would begin the real task which cosisted of 20 trials. After completing the task with either the feature or conjunction search, participants would then repeat the task in the remaining condition. This took approximately 20 minutes.

@@

### Eye Movements
`r num_fixations` fixations were recorded. Of these, `r num_removed` fell outside of the stimuli area and were removed. Fixations landing within a vertical strip consisting of 10% of the stimuli's width were classed as central. All remaining fixations were then classed as landing on the homogeneous or heterogeneous half of the stimulus. Initial fixations were not included in the analysis. Numbers of fixations are given in Table \ref{tab:table}.

>>>>

# Methods 
The experiment took part over two sessions, each lasting approximately 1 hour. All participants reported normal or corrected to normal vision and were from the University of Aberdeen. Participants were either compensated with course credit or £15 for their time. All participants gave informed consent.

All tasks were completed on a 17-inch CRT monitor with a resolution of 1400$x$1050 (*n* = 40) or 1600$x$1200 (*n* = 24). All tasks were programmed in MATLAB (which version?) using psychtoolbox and eyelinktoolbox.

## Split-Half
This task lasted approximately 30 minutes and was carried out in both sessions. A chin rest with forehead bar ensured a viewing distance of 47cm. Participants' fixations were tracked using a deskmounted Eylink 1000 to record eye position at 1000 Hz. Prior to every block, a 9-point calibration was carried out. Participants were instructed to state the presence, or absence, of a small target line segment that was tilted 45&deg; to the right. The distractor line segments (how many, i.e. how many rows/columns?) were arranged in such a way to create a "hard" and "easy" search side. The mean orientation of the distractors was orthogonal to the target orientation, with either a low variance (18&deg;) which created a relatively homogenous texture ("easy" side), or a high amount of variance (95&deg;) creating a more heterogeneous texture ("hard" side). Each line segment subtended approximately 1.6&deg; of visual angle. For 50% of the trials, there was a target present. Participants were told to report (how?) whether the target was present or absent on each trial as quickly and as accuractely as possible.

@@

## Adaptive Choice
For this task, participants viewed the display from approximately 47cm away, but no chin rest was used to ensure a constant viewing distance. The search display consisted of small red, blue, and green squares arranged in three rings around a fixation point (how many of each colour?). the squares subtended between ~1.1&deg; and ~1.3&deg; depending on the screen resolution the participant was tested at (either 1600$x$1200 or 1400$x$1050, respectively). The participants' task was to find either a blue or a red square that contained a number between 2 and 5 inclusive. On every trial, just one blue and one red square contained a number between 2 and 5. Participants were instructed to find and report one of them. To ensure we could tell which colour they had decided, the blue and red target squares would always have a different number inside. The distractor blue and red squares would always contain numbers between 6 and 9. The green squares contained numbers between 2 and 9. Participants were instructed to complete the task as quickly and as accurately as possible.

Before starting the task, participants were given 10 practice trials and were free to ask any questions before starting the main expriment. If a participant reported a number that was not in one of the two target boxes, a tone would sound to alert them to their mistake. (How many trials in the experiment?)

At the beginning of the experiment, there would be more red than blue squares (**need to check this is accuracte**) for five trials. Then, across the next seven trials, the red squares would gradually change from red to blue, stay blue for five trials, and then change from blue to red across seven trials, stay red for five trials, and so on. The number of green squares was constant. After completing the task, participants were then asked to fill out a short three-item questionnaire asking them about their strategy and whether they noticed the gradual shift from one colour being the majority to the other.

## Foraging 
Viewing distance was approximately 47cm (no chin rest was used). At the beginning of each trial, participants were presented with 84 small shapes on the screen which subtended between ~0.6&deg; and ~0.7&deg; depending on the screen resolution the participant was tested at (either 1600$x$1200 or 1400$x$1050, respectively). Half of these were target items that participants were to click on, using the mouse cursor, until they had "collected" all of them (they disappeared when clicked). There were two types of search with this task. In feature search, participants were presented with circles of 4 different colours (red, blue, yellow, and green) and were instructed to click on all circles of two of the colours (e.g. click on the red and green, not the blue and yellow). In conjunction search, there were squares and circles coloured with two of the four possible colours, for example, they could be instructed to collect the blue squares and yellow circles, but to avoid the blue circles and yellow squares. In both conditions, if participants clicked on a non-target shape the trial immediately ended and re-started with 84 shapes in a new set of locations. Participants completed both of these conditions and the order was counterbalanced with the colours of the targets being randomised across participants.

Before starting the experiment, participants had 5 practice trials to familiarise themeselves with the task, after which they would begin 20 experimental trials. After completing the task with either the feature or conjunction search, participants would then repeat the task in the remaining condition. This took approximately 20 minutes.

@@

### Eye Movements
`r num_fixations` fixations were recorded. Of these, `r num_removed` fell outside of the stimulus area and were removed. Fixations landing within a vertical strip consisting of 10% of the stimuli's width were classed as central. All remaining fixations were then classed as landing on the homogeneous or heterogeneous half of the stimulus. Initial fixations were not included in the analysis. Numbers of fixations are given in Table \ref{tab:table}.
